Predicting Diabetes Based on Various Factors Using Decision Tree Analysis

### 2023-12-15 manuscript/manuscript.tex
update of confusion Matrix
Some reformatting
Addition of keywords and confusion matrix explanation

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

@@

@@

>>>>

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{indentfirst}

@@

\section*{Keywords}
Decision Trees, Diabetes, Machine Learning,

@@

Finally we can now look at Figure~ref{fig:Heatmap}, to see the confusion matrix heatmap for our decision tree analysis. Out of the 371 patients that had an outcome
of not having diabetes, the model correctly identified 318 of them. Whereas it only incorrectly said that they did not have diabetes when in fact they did 53 times. 
In terms of predicting that the patients had diabetes, the model predicted 136 patients had diabetes out of the 183 that actually did. In turn it precicted that 47 of the
patients did not have diabetes when in fact they did. This shows that the model does a pretty good job in identify if the patient has diabetes but does an even better job
identifying when the patient does not have diabetes.
